### 2023-12-19 documentation/thesis/thesis_document.tex
more thesis

@@

\begin{itemize}
\item
  mbed
\item
  automatic sensor detation ablaufdiagramm erst nach i2c geräte scannen
  dann analog versuchen
\item
  serial cli support for manual mode
\item
  sync impulse =\textgreater{} 1 mastersensor als taktqelle
\item
  interene mittelung und speichern der werte im buffer ringubber welcher
  bei jedem sync impuls neu belegt wird
\item
  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{1}
  \tightlist
  \item
    core übernimmt mittelung und auswetung
  \end{enumerate}
\item
  was durch den user implementiert werden muss klasse
\end{itemize}

\ref{Unified_sensor_firmware_simplified_program_strucutre.png}

\ref{lst:CustomSensorClass}

@@

\hypertarget{sensor-syncronsisation-interface}{%
\section{Sensor syncronsisation
interface}\label{sensor-syncronsisation-interface}}

@@

\hypertarget{example-sensors}{%
\section{Example Sensors}\label{example-sensors}}

@@

\hypertarget{integration-of-an-industry-teslameter}{%
\subsection{Integration of an industry
Teslameter}\label{integration-of-an-industry-teslameter}}

@@

\hypertarget{multi-sensor-setup}{%
\subsection{Multi-Sensor setup}\label{multi-sensor-setup}}

@@

Another important aspect when using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the \gls{usb} interface. If
several sensors are connected locally, they can be connected to each
other via their sync input using short cables. One sensor acts as the
central clock (see chapter \ref{sensor-syncronsisation}). this no longer
works for long distances and the syncronisation must be made via the
network connection.

@@

\begin{itemize}
\tightlist
\item
  nummerieierung zuerst lokale sensoren dann weitere proxy sensoren
\item
  commando templating
\end{itemize}

@@

In the first version of this \gls{mrp}-library, the user had to write
his own Python scripts even for short measurement and visualisation
tasks. However, this was already time-consuming for reading out a sensor
and configuring the measurement parameters and metadata and quickly
required more than 100 lines of new Python code. Although such examples
are provided in the documentation, it must be possible for programming
beginners in particular to use them. To simplify these tasks, a
\gls{cli}\ref{example_measurement_analysis_pipeline.png} was implemented
around this \gls{mrp}-library, which is then also supplied as a fixed
component. This \gls{cli} implements the following functionalities:

@@

Thanks to this functionality of the \gls{cli}, it is now possible to
connect a sensor to the \gls{pc}, configure a measurement series with it
and run it at the end. The result is then an exported file with the
measured values. These can then be read in again with the
\gls{mrp}-library and processed further. The bash
code\ref{lst:mrpcli_config_run} shows this procedure in detail.

>>>>

Microcontroller firmware is software that is executed on a
microcontroller in embedded systems. It controls the hardware and
enables the execution of predefined functions. The firmware is used to
process input data, control output devices and fulfil specific tasks
according to the program code. It handles communication with sensors,
actuators and other peripheral devices, processing data and making
decisions. Firmware is critical to the functioning of devices.

@@

The firmware is responsible for detecting the possible connected
sensors\ref{Implemented_digital_halleffect_sensors.csv} and reading them
out. This measured data can be forwarded to a host \gls{pc} via a user
interface and can then be further processed there. An important
component is that as many common sensors as possible can be easily
connected without having to adapt the firmware. This modularity was
implemented using \passthrough{\lstinline!abstract!} class design. These
are initiated according to the sensors found at startup. If new hardware
is to be integrated, only the required
functions\ref{lst:CustomSensorClass} need to be implemented.

@@

The flow
chart\ref{Unified_sensor_firmware_simplified_program_strucutre.png}
shows the start process and the subsequent main loop for processing the
user commands and sensor results. When the microcontroller is started,
the software checks whether known sensors are connected to \gls{i2c} or
\gls{uart} interfaces. If any are found (using a dedicated \gls{lut}
with sensor address information), the appropriate class instances are
created and these can later be used to read out measurement results.

Next, the subsystem for multi-sensor
synchronisation\ref{sensor-syncronsisation-interface} is set up. The
last step in the setup is to set up communication with the host or
connected \gls{pc}. All microcontroller platforms used here have a
\gls{usb} slave port. The used usb descriptor is
\passthrough{\lstinline!Serial over (+usb)!}- ((+usb)\gls{cdc}). This is
used to emulate a virtual RS232 communication port using a USB port on a
\gls{pc} and usually no additional driver is needed on modern systems.

Now that the setup process is complete, the system switches to an
infinite loop, which processes several possible actions. One task is, to
react to user commands which can be sent to the system by the user via
the integrated \gls{cli}. All sensors are read out via a timer interval
set in the setup procedure and their values are stored in a ringbuffer.
Ring buffers, offer efficient data management in limited memory. Its
cyclic structure enables continuous overwriting of older data, saves
memory space and facilitates seamless processing of real-time data. Ring
buffers are well suited for applications with variable data rates and
minimise the need for complex memory management. The buffer can be read
out by command and the result of the measurement is sent to the host.

\hypertarget{sensor-syncronsisation-interface}{%
\subsection{Sensor syncronsisation
interface}\label{sensor-syncronsisation-interface}}

\begin{itemize}
\tightlist
\item
  sync impulse =\textgreater{} 1 mastersensor als taktqelle
\item
  interene mittelung und speichern der werte im buffer ringubber welcher
  bei jedem sync impuls neu belegt wird
\item
  ringbuffer
\end{itemize}

\%\%Unified\_sensor\_firmware\_multi\_sensor\_synchronisation\_procedure.drawio.png\%\%

\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure.drawio.png}

@@

\hypertarget{example-sensors}{%
\section{Example sensors}\label{example-sensors}}

@@

\hypertarget{integration-of-an-industry-teslameter}{%
\subsection{Integration of an industry
teslameter}\label{integration-of-an-industry-teslameter}}

@@

\hypertarget{multible-sensor-setup}{%
\subsection{Multible sensor setup}\label{multible-sensor-setup}}

@@

Another important aspect when using several sensors via the proxy system
is the synchronisation of the measurement intervals between the sensors.
Individual sensor setups do not require any additional synchronisation
information, as this is communicated via the \gls{usb} interface. If
several sensors are connected locally, they can be connected to each
other via their sync input using short cables. One sensor acts as the
central clock as described in\ref{sensor-syncronsisationiinterface}.
this no longer works for long distances and the syncronisation must be
made via the network connection.

@@

\begin{itemize}
\item
  nummerieierung zuerst lokale sensoren dann weitere proxy sensoren
\item
  commando templating
\item
  einzelne sensor capabilites werden gemerged
\item
  ids werden aufsuimmiert
\item
  spätere sensor identifikation geschieht über die jeweilige sensor id,
  welche über diesen index abgefragt werden kann
\item
  tablle mit mergin algorithmus
\end{itemize}

@@

In the first version of this \gls{mrp}-library, the user had to write
his own Python scripts even for short measurement and visualisation
tasks. However, this was already time-consuming for reading out a sensor
and configuring the measurement parameters and metadata and quickly
required more than 100 lines of new Python code. Although such examples
are provided in the documentation, it must be possible for programming
beginners in particular to use them. To simplify these tasks, a
\gls{cli}\ref{example_measurement_analysis_pipeline.png} was implemented
around this \gls{mrp}-library. The (+mrp)-library-\gls{cli} implements
the following functionalities:

@@

Thanks to this functionality of the \gls{cli}, it is now possible to
connect a sensor to the \gls{pc}, configure a measurement series with it
and run it at the end. The result is then an exported file with the
measured values. These can then be read in again with the
\gls{mrp}-library and processed further. The following bash
code\ref{lst:mrpcli_config_run} shows the setup procedure in detail:
